---
name: Thong Hoang
surname: Trinh
position: "Software Test Engineer"
address: "District 12, Ho Chi minh"
phone: +84 372 725 338
email: "trinhhoangthong1503@gmail.com"
output: 
  vitae::moderncv:
    theme: classic
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

library(vitae)
library(tibble)
library(dplyr)
library(stringr)
library(tidyr)
```

# Objectives

* Seeking opportunity to learn methods for effectively planning and contribute to testing high-quality applications.
* Eager to apply my analytical and problem-solving abilities to contribute to optimized code meeting business requirements.
* Motivated to learn from experienced engineers and become proficient in industry tools and processes.
* Aiming to develop communication and teamwork abilities in a professional environment and gain valuable experience at workplace.


# Some stuff about me

 * Continuous Self-Improvement: I believe in continuous self-improvement and strive to be better today than I was yesterday. This drive fuels my personal and professional growth.
 
* Entrepreneurial Spirit: In 2017, I took a gap year and channeled my entrepreneurial spirit to open my own takeaway cafe. This venture honed my skills in business management, customer service, and problem-solving.

 * Resilience and Adaptability: My gap year experience taught me to be resilient in the face of challenges and adaptable to changing circumstances.

# Education

```{r }
tribble(
  ~ Degree, ~ Year, ~ University, ~ Location, ~ Grade,
  "Bachelor, PHYSICS AND ENGINEERING PHYSICS", "2023", "VNUHCM - UNIVERSITY OF SCIENCE", "Ho Chi Minh City", "GPA: 7.21/10, Thesis: 9.5/10, Rank: 2nd in class",
   "Intermediate professional, NETWORK AND SYSTEM ADMINISTRATION/ADMINISTRATOR", "2017", "Information and Mass Communication Institute of Ho Chi Minh City (IMC)","Ho Chi Minh City",NA
) %>%
  detailed_entries(Degree, Year, University, Location, Grade)

```

# Relevant Coursework

```{r }
tribble(
  ~ Degree, ~ Year, ~ University, ~ Location, ~ Grade,
  "ENGINEERING PHYSICS", "", "", "", " Quantum Mechanics, Electromagnetism, Thermodynamics, Solid State Physics, Optics, Nuclear Physics, Mathematical Physics, Introduction to Electronics, Semiconductor Devices, Semiconductor Optoelectronics",
   "SYSTEM ADMINISTRATION","","","","Operating Systems, Network Design and Administration, Computer Security, Database Management, Data Structures and Algorithms"
) %>%
  detailed_entries(Degree, Year, University, Location, Grade)

```

# Technical Skills

```{r}
tribble(
  ~ Skill,
  "Programming language: R, C++, SQL, Python",
  "Software: Proteus Design Suite, VMware, Matlab, Excel, R Studio, Originlab, Tableau, Visual Studio Code",
  "Operating system: Windows server, Linux CentOS, Ubuntu"
) %>%
  brief_entries(Skill)

```

# Projects

* Effect of the growth sector boundary on the structure and characteristics of KDP crystals grown from crystal violet and EDTA added mother solution", "2023

  + Demonstrate the optimal CV(Crystal Violet) concentration for enhancing the second harmonic generation (SHG) performance in KDP crystals
  
  + The development process of the KCVE (0.001 mol%) single crystal rod is simulated using Matlab. 
  
  + The KCVE samples are analyze by EDX spectra, XRD analysis, and measurements such as UV-Vis spectra, PL spectra, and second harmonic generation (SHG) effects. 
 
 (https://github.com/TomALtR/my_thesis_matlab)
 
* ZNO THIN FILM COATING
  + Using sputtering, sol-gel dip coating method to coat material.
  + Applied XRD, EDX and UV-Vis to analyze the properties of each method.
  
  
* STUDENT ATTENDANCE PROGRAM
  
  + Matlab project that apply Knowlegde learn through out the matlab programing subject.
  + Import files from excel to find the right data in both ID number and name then import back the new data to excel sheets.
  
 (https://github.com/TomALtR/my_matlab_first_project)
 
# Certifications

```{r}
tribble(
  ~ Certification, ~ Year, ~ Authority,
  "TOEIC 600", "2017", "ETS",
  "Learning How to Learn: Powerful mental tools to help you master tough subjects" , "2020", "Coursera",
  "Ask Questions to make Data-Driven Decisions", "2022", "Coursera",
  "Analyze Data to Answer Questions","2022","Coursera",
  "Data Analysis with R Programming" , "2023", "Coursera",
  "Google Data Analytics Certificates", "2023", "Coursera",
  "Technical Support Fundamentals","2023","Coursera",
  "Crash Course on Python","2023","Coursera",
) %>%
  brief_entries(Certification, Year, Authority)

```

# Experience

```{r }
tribble(
  ~ Degree, ~ Year, ~ University, ~ Location, ~ Grade,
  "English Teacher", "12-2022", "Edupia Tutor", "", "Utilized technology to enhance instruction, increase student engagement, and provide real-world learning experiences",
) %>%
  detailed_entries(Degree, Year, University, Location, Grade)

```

## This CV was generated using R
(https://github.com/TomALtR/my_CV/tree/main/Rstudio_CV)